Very Large Integers and polynomial inner products

### 2013-01-16 doc/paper_vli/vli.tex
paper

--------------------------------------------------------

@@

\begin{itemize}
\item  We goal of this library is performed efficient arithmetic for polynomial with large coefficient and execute efficient inner product : multithread and/or GPU.
\item give an efficient library for the HP2C initiative code .e.g  HTSE
\end{itemize}
--------------------------------------------------------

@@

\begin{itemize}
\item  We does not use SIMD 
\item because the contiguous data does not help at all for CB propagation
\item 
%The disagreement  of this choice, the AoS order does not facilitate the usage of the SIMD instruction such as the AVX instructions of the Sandy Bridge x86-64 architecture.
%Applying SIMD to the AoS, for an addition or a subtraction is a nonsense because there is no specific instruction to propagate carry bit between entries of the SIMD register.
%It could be  apply  on multiplications for integer  larger than 1024-bit \cite{SIMD}, unfortunately, it does not correspond to our working range. Consequently, we do not 
%use the multimedia instruction into the ASM kernels.
\end{itemize}

@@

\subsubsection{module vector}
\begin{itemize}
\item +- std::vector
\end{itemize}

@@

\begin{itemize}
\item object conception imposes SoA
\item AoS is the good for SIMD ( global solution)
\item  with the flexibility of module we lost the SIMD 
\end{itemize}

@@

\subsubsection{CPU implementation}
\begin{itemize}
\item   explain quickly ..... just loop other coefficient 
\item  with the OMP 
\end{itemize}
%In terms of  programming and parallelization, in the CPU version, the previous equations can be reduced to independent loops with a final reduction.
%The CPU parallelization has been done with OpenMP. The OpenMP threads calculate several  polynomial multiplications and make a local reduction. At the end, a final reduction is performed  by the main thread.

@@

\begin{itemize}
\item both algo can be mix -> hybrid mode
\item a few line to explain how does it work
\end{itemize}
%We also developed an optional hybrid mode between CPU/GPU. This  technique is usual in GPU computing.
%We split the input vectors of polynomials into two chunks of data, execute concurrently on CPU and GPU. 
%A synchronization  is performed during  the memory transfer   by the final reduction, at the end of the calculation.

>>>>

@@

\begin{itemize}
\item  We goal of this library is performed efficient arithmetic for polynomial with large coefficient and execute efficient inner product : multithread and/or GPU.
\item give an efficient library for the HP2C initiative code .e.g  HTSE
\end{itemize}

@@

\begin{itemize}
\item We does not use SIMD for kernels 
\item because the contiguous data does not help at all for CB propagation 
\item It could be  apply  on multiplications for integer  larger than 1024-bit \cite{SIMD}, unfortunately, it does not correspond to our working range.

%Consequently, we do not  use the multimedia instruction into the ASM kernels.

%The disagreement  of this choice, the AoS order does not facilitate the usage of the SIMD instruction such as the AVX instructions of the Sandy Bridge x86-64 architecture.
%Applying SIMD to the AoS, for an addition or a subtraction is a nonsense because there is no specific instruction to propagate carry bit between entries of the SIMD register.
%It could be  apply  on multiplications for integer  larger than 1024-bit \cite{SIMD}, unfortunately, it does not correspond to our working range. Consequently, we do not 
%use the multimedia instruction into the ASM kernels.
\end{itemize}

@@

\subsubsection{module vector}
\begin{itemize}
\item derived from  std::vector
\end{itemize}

@@

\begin{itemize}
\item object conception imposes SoA
\item AoS is the good for SIMD ( global solution) but for this solution modules disappear, we loose all the flexibility
\item  Do SoA to AoS reorganization of the data costs too much, Maybe intel Xeon phi could be a solution in the future, as gpu we could develop a booster
\end{itemize}

@@

\subsubsection{CPU implementation}
\begin{itemize}
\item   explain quickly ..... just loop other coefficient 
\item  explain the implementation of threadings basic OMP
\end{itemize}
%In terms of  programming and parallelization, in the CPU version, the previous equations can be reduced to independent loops with a final reduction.
%The CPU parallelization has been done with OpenMP. The OpenMP threads calculate several  polynomial multiplications and make a local reduction. At the end, a final reduction is performed  by the main thread.

@@

\subsubsection{hybri-mode}

\begin{itemize}
\item both algo can be mix  $=>$ hybrid mode
\item a few line to explain how does it work
\end{itemize}
%We also developed an optional hybrid mode between CPU/GPU. This  technique is usual in GPU computing.
%We split the input vectors of polynomials into two chunks of data, execute concurrently on CPU and GPU. 
%A synchronization  is performed during  the memory transfer   by the final reduction, at the end of the calculation.
